Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Simplify a proof.

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$,  $\sigrets \subseteq \gsigrets$, $\sigcloss \subseteq \gsigcloss$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma \not\nequal (\lrv \circ \xi)$.
\end{lemma}
\begin{proof}
  Consider the following two cases:
  \begin{itemize}
  \item $\sigma \in \sigrets$:

    In this case, we have that $\npair[0]{\left(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1)\right)}$ is not in $\lrv(\xi(\hat{W}))$, but we can show that it is in $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma~\hat{W}$ by taking a $\hat{W}$ such that the following hold:
    \begin{itemize}
    \item $\sigrets \subseteq \gsigrets$: assumption.
    \item $\dom(\code) \subseteq \ta$: assumption.
    \item $\exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]}$ such that $\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen)$, $\dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr]$, $\decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$, $\code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets$.
      It is not difficult to construct a $\hat{W}$ with a suitable $\spatialo$ region to satisfy these conditions. 
    \end{itemize}

  \item $\sigma \in \sigcloss$: This follows easily from the definition of $\codereg{}$ and Lemma~\ref{lem:lrvtrusted-not-nequal-lrvuntrusted}.
  \end{itemize}
\end{proof}

>>>>

\begin{lemma}
  \label{lem:codereg-Hsigma-not-lrv}
  If $\dom(\code) \subseteq \ta$,  $\sigrets \subseteq \gsigrets$, $\sigcloss \subseteq \gsigcloss$, $n > 0$ and $\sigma \in (\sigrets \uplus \sigcloss)$, then $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}.H_\sigma~ \sigma \not\nequal (\lrv \circ \xi)$.
\end{lemma}
\begin{proof}
  Consider the following two cases:
  \begin{itemize}
  \item $\sigma \in \sigrets$:

    % In this case, we can choose a $b,e$ and construct a $\hat{W}$ such that $\npair[0]{\left(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1)\right)}$ is not in $\lrv(\xi(\hat{W}))$, but it is in $\codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}.H_\sigma~ \sigma~\hat{W}$.
    % It suffices to make choices for $b,e$ and $\hat{W}$ such that the following hold:
    % \begin{itemize}
    % \item $\sigrets \subseteq \gsigrets$: assumption.
    % \item $\dom(\code) \subseteq \ta$: assumption.
    % \item $\exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]}$ such that $\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen)$, $\dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr]$, $\decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$, $\code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets$.
    %   It is not difficult to construct a $\hat{W}$ with a suitable $\spatialo$ region to satisfy these conditions.
    % \end{itemize}
    %  DOMI: what if code has no call or no seal?
    It suffices to observe that $\npair[0]{(0,0)} \in \lrv(\xi(\hat{W}))$ but not $\npair[0]{(0,0)} \in \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb,\gsigrets,\gsigcloss)}.H_\sigma~ \sigma~ \hat{W}$.

  \item $\sigma \in \sigcloss$:
    TODO: UPDATE

    This follows easily from the definition of $\codereg{}$ and Lemma~\ref{lem:lrvtrusted-not-nequal-lrvuntrusted}.
  \end{itemize}
\end{proof}
